---
title: "Behavioral analysis name_hider_experiment_pilot1"
author: "Robbert van der Mijn"
date: "03/03/2022"
output: 
  html_document: 
    highlight: kate
    theme: spacelab
    toc: true
    code_folding: hide
    toc_float: 
        collapsed: false
        smooth_scroll: true
    number_sections: true
editor_options: 
  chunk_output_type: console
---

# Description dataset

Load pre-processed data:

```{r}
library(data.table)
library(ggplot2); theme_set(theme_classic())
load("20220309165755_36pps_cit_bch_dec21_targetBL.rdata")
```

# Demographics

```{r}
demdat <- NULL
files <- Sys.glob("../data/*.csv")
for(f in files){
  d <- fread(f)
  demdat <- rbind(demdat, d, fill = T)
}

demdat[count_trial_sequence == 0, .N, by = sex]
demdat[count_trial_sequence == 0, .(age = mean(age), sd = sd(age))]
```

# Behavioral results

```{r}
bdat <- dat[time == 0 & trial > 0] # one row per trial, remove practice trials
sum_bdat <- rbind(bdat[, .(correct = mean(T1_correct), target = "T1"), by = .(subject_nr, T1)],  bdat[, .(correct = mean(T2_correct), target = "T2"), by = .(subject_nr, T1)])

ggplot(sum_bdat[, .(correct = mean(correct), se = sd(correct)/sqrt(.N)), by = .(T1, target)], aes(x = T1, y = correct)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = correct - se, ymax = correct + se), width = .3) +
  facet_wrap(~target)
```

If participant would respond with a random button each trial, control, no_target and secret_target would be 75% acc and target would be 25%.

What about liers and truthers?

```{r}
sum_bdat_lie <- rbind(bdat[, .(correct = mean(T1_correct), target = "T1"), by = .(subject_nr, T1, lie)],  bdat[, .(correct = mean(T2_correct), target = "T2"), by = .(subject_nr, T1, lie)])

ggplot(sum_bdat_lie[, .(correct = mean(correct), se = sd(correct)/sqrt(.N)), by = .(lie, T1, target)], aes(x = T1, y = correct, fill = lie)) +
  geom_bar(stat = "identity") +
  geom_errorbar(aes(ymin = correct - se, ymax = correct + se), width = .3) +
  facet_grid(lie ~ target)
```

# Conclusion

The task is relatively easy. Guessing a target correct based on chance will yield 75% correct on "control", "no target" and "secret target" trials and 25% correct on "target" trials. It was easier for the "truth" participants (their real name was the target) to spot the target that for the "lie" participants (they chose a fake name as target). 